\section*{Experience}
\begin{tabular}{l r}
	\textbf{Virtustream (Dell EMC)} & Summer of 2018 - Present \\
\end{tabular}
\begin{itemize}
	\item Responsible for the design and maintenance of a next generation PaaS for internal customers.
	\item Improved developer efficiency by creating custom Kubernetes controllers
\begin{tabular}{l r}
	\textbf{LogicMonitor} & Summer of 2016 - Summer of 2018 \\
\end{tabular}
\begin{itemize}
	\item Responsible for maintaining a SaaS platform composed of 12 different microservices across AWS and physical datacenters.
	\item Responded to service disruptions and outages in an on-call rotation.
	\item Enabled the development team to iterate faster and operations to scale by architecting and implementing a standardized CI/CD pipeline.
	\item Streamlined the management of Kubernetes clusters by developing Terraform modules for cluster creation.
	\item Increased application resiliency of over 10 production Tomcat applications by working with developers on migrating the applications into Kubernetes.
	\item Created an integration of LogicMonitor with Kubernetes that is now the official solution for LogicMonitor customers wanting to monitor Kubernetes. \newline {\small\href{https://github.com/logicmonitor/k8s-argus}{https://github.com/logicmonitor/k8s-argus}}
	\item Established a set of data collection methods for Kubernetes that are now used in tandem with Argus.
	\item Worked with the product team on new features meant to help in monitoring ephemeral resources like containers, a feature that customers have long asked for.
	\item Generated sales by interfacing with potential and exsting customers that wanted to monitor Kubernetes using LogicMonitor, and providing training and feedback to our sales team.
	\item Enabled the operations team to be more agile and responsive to capacity issues by writing a capacity management tool that automated a large number of manual processes.
\end{itemize}
\begin{tabular}{l r}
	\textbf{Gooru - Internship} & Summer of 2011 \\
\end{tabular}
\begin{itemize}
	\item Created in-house tools that improved workplace productivity.
	\item Setup and maintained linux servers responsible for various workplace tasks.
	\item Wrote data scraping scripts in python.
\end{itemize}

\begin{tabular}{l r}
	\textbf{Personal projects} &   \\
\end{tabular}
\begin{itemize}
	\item \textbf{Kubernetes}: Official member of the Kubernetes community.
	      \newline{\small \href{https://github.com/kubernetes/kubernetes/pulls/andrewrynhard}{https://github.com/kubernetes/kubernetes/pulls/andrewrynhard}}
	\item \textbf{Autonomy}: An organization dedicated to creating automation tools.
	      \newline{\small \href{https://github.com/autonomy}{https://github.com/autonomy}}
\end{itemize}
